### 2023-09-21 5.Conclusions/further.tex
More changes, arriving in paris...

>>>>

Training directly on the chip has a great advange over external training. Indeed training within the chip will allow to completely ignore the wires own resistance in the crossbar array. This is because they will an integral part of the weights, if the weight needs to be lowered then the resistance will be raised (because the conductances need to be lowered). %TODO finish with better explainnation
